---
title: "flat_first.Rmd for working package"
output: html_document
editor_options: 
  chunk_output_type: console
---

<!-- Run this 'development' chunk -->
<!-- Store every call to library() that you need to explore your functions -->

```{r development, include=FALSE}
library(testthat)
```

<!--
 You need to run the 'description' chunk in the '0-dev_history.Rmd' file before continuing your code there.

If it is the first time you use {fusen}, after 'description', you can directly run the last chunk of the present file with inflate() inside.
--> 

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

# Include some data examples in your package

<!-- 
 Store your dataset in a directory named "inst/" at the root of your project.
 Use it for your tests in this Rmd thanks to `pkgload::load_all()` to make it available
and `system.file()` to read it in your examples.

- There already is a dataset in the "inst/" directory to be used in the examples below
-->
# model_config
    
```{r function-model_config}
#' model_config
#' 
#' config models and test
#' @param provider default as openai
#' @param path the path url 
#' @param label the label of defined model
#' @param model the used model
#' @param file the saved yaml file
#' @param test_apikey the api key for model test 
#' @return yamlfile
#' 
#' @export
model_config <- function(provider = "OpenAI - Chat Completions",
                         path = "https://api.lingyiwanwu.com/v1/chat/completions",
                         label = "yi-34b-chat-0205 (01.AI)",
                         model = "yi-34b-chat-0205",
                         file = "dev/model_test.yml",
                         test_apikey
                         ){
  model_temple <- chattragents::model_temple
  model_temple$default$provider <- provider
  model_temple$default$path <- path
  model_temple$default$label <- label
  model_temple$default$model <- model
  fs::dir_create(path = dirname(file))
  yaml::write_yaml(model_temple,
                   file = file)
  message("configing model,now test ...")
  Sys.setenv("OPENAI_API_KEY" = test_apikey)
  chattr::chattr_use(file)
  chattr::chattr("who are you")
  return(file)
}
```
  
```{r example-model_config}

```
  
```{r tests-model_config}
test_that("model_config works", {
  expect_true(inherits(model_config, "function")) 
})
```
  

# chattragent_use
    
```{r function-chattragent_use}
#' chattragent_use
#' 
#' chattr agent setting
#' @param agent the agent name in the dataset
#' @return agent
#' 
#' @export
chattragent_use <- function(agent){
    agentlist <- chattragents::agentlist
    agent <- agentlist[grepl(agent,agentlist)]
    if (length(agent) == 0){
      stop("agent is not found in the current dataset")
    } else if(length(agent) > 1){
      message(glue::glue("{length(agent)} agents found"))
      for (i in 1:length(agent)){
        message(glue::glue("{i}.{agent[i]}"))
      }
      id <- readline("multiagents found,choose one :") %>% 
        as.numeric()
      if (id >=1 && id <= length(agent)){
        agent <- agent[id]
      }else{
        stop("error! choose a correct number.")
      }
    }
    agent <- glue::glue("agents/{agent}.txt") %>% 
      system.file(package = "chattragents")
    if (!file.exists(agent)){
      stop("agent is not found in the current dataset")
    } else {
      chattr::chattr_defaults(prompt = readLines(agent))
    }
    return(chattr::chattr_defaults())
}
```
  
```{r example-chattragent_use}

```
  
```{r tests-chattragent_use}
test_that("chattragent_use works", {
  expect_true(inherits(chattragent_use, "function")) 
})
```
  
<!--
# There can be development actions

Create a chunk with 'development' actions

- The chunk needs to be named `development` or `dev`
- It contains functions that are used for package development only
- Note that you may want to store most of these functions in the 0-dev_history.Rmd file

These are only included in the present flat template file, their content will not be part of the package anywhere else.
-->

```{r development-inflate, eval=FALSE}
# Keep eval=FALSE to avoid infinite loop in case you hit the knit button
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_first.Rmd", vignette_name = "Get started")
```


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory
